\section{Conclusion}

This work presented Medscope, an end-to-end diagnostic system comprising hardware, mobile, and cloud components that enable accessible point-of-care imaging. The platform couples an image acquisition device based on a microcontroller, a mobile app that handles configuration and communication, and a back-end service with standardized preprocessing and AI-aided analysis. By using event-driven image capture and a direct TCP connection between the microcontroller and the mobile device, the system avoids the complexity and energy requirements of continuous streaming while sustaining image fidelity appropriate for clinical inference.

Among these, the mobile application plays the central role, serving both as the user interface and as a network endpoint for receipt, validation, and forwarding of images. Images sent to the backend are then processed using consistent normalization and model inference routines to minimize variability and support reliable predictions. The inclusion of models trained on more diverse datasets, especially for dermatoscopy, helps address some persistent gaps in skin-tone representation common in traditional dermatology benchmarks. Together, these components form a consistent and practical pipeline to deliver medical imaging support on resource-constrained hardware while providing seamless integration with cloud-based diagnostic applications. Further development will target enhancing robustness across variable capture conditions, increasing dataset coverage, and reinforcing interoperability between the embedded devices, mobile clients, and backend systems.
